\pkg{SVMBridge}: Using SVM Solvers from R

### 2015-09-15 paper/article.tex
update paper

@@

Predicting from a trained model is rather easy, as there are usually not many options.
As with training, the predict routine will accept a model either in memory or from a file.

@@

@@

...

@@

@@

@@

@@

As only LIBSVM models are being used, one can readily use the 
inbuild functions of the SVMBridge.

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> model = trainSVM (method = "LIBSVM", cost = 1.0, gamma = 2.0,
			trainDataFile = "./data.sparse",
			epsilon = 0.042,
			modelFile = modelFile,
			useBias = TRUE,
			verbose = verbose
		)
\end{CodeInput}
\begin{CodeOutput}
...
\end{CodeOutput}
\end{CodeChunk}

The training data can be passed on via a variable in memory or by specifying the path 
of the data set file. 
Note that there are two sets of variables: Those who belong to the SVMBridge,
like the trainDataFile variable or verbose flag, and those that are passed further
to the underlying SVM wrapper.
Not all options that are provided by the underlying SVM solver
are supported by the wrappers. As our focus lies on binary classification, because of time constraints 
we opted  to support only these options, e.g. we dropped the one-class SVDD in LIBSVM.
In case there is need for other options, it is 
easy to enhance the wrappers.
There is furthermore the subsampling option, which can be used for larger data sets.

@@

Predicting from a trained model is rather easy, as there are usually not many options.
As with training, the predict routine will accept a model either in memory or from a file.
The same is true for the data to predict.  Again notice that data and models in memory 
must be written to disk prior to calling the prediction binary.

@@

Specifically, this routine compute the following values:
\code{weight} is given by $\frac{1}{2} w^T w$, with
$w = \sum_i \alpha_i s_i$. Furthermore, we have
that $C \sum_i max (0, 1 - ..) $, and 
\code{primal} is then given by $primal = w + CHinge$.
\code{dual} on the other hand is simply
$w - \sum_i |\alpha_i|$. In general it must hold
that $primal \geq dual$. 
WHAT IF NOT? what does it mean?

@@

A few routines have been placed into the package that were helpful
with testing. Namely, there are several generators for synthetical data sets,
collected from different publications. 
WHAT ELSE? can routines be used outside? detectTilde e.g.?

@@

The flow is as follows: The SVMBridge will call 
createTrainingArguments method of any wrapper. The wrapper
will return a string that contains all parameters that need to be
passed to the binary of the underlying SVM solver. Note that
this includes the model, prediction and training files.

@@

A simple S3 method has to be created that needs to be called
\code{createTrainingArguments.LIBSVM}. Apart from the very
first argument (taking the object itself), all other paramters
can be chosen freely. After training, from the output several
training information will be extracted by the 
\code{extractTrainingInfo()} function.

@@

Similar to the training call, \code{createTestArguments()} needs to
writen. Again, it should accept three variables called testDataFile and
modelFile as well as predictionFile. There is also a
\code{extractTestInfo()} that will extract the important informations
from the output of the test binary.

@@

As only LIBSVM models are being used, one can readily use the 
inbuild functions of the SVMBridge. If the solver works with its
own model, one needs to rewrite the readModel method of the wrapper.
This will only obtain the modelFile and will return the model
in the model format (S3 Object with XY, describe it somewhere else)
SVMBridge needs also a writeModel functions, as models passed in
memory needs to be written to disk. .
Finally it is necessary to access the predictions itself. For this one
needs to write the \code{readPredictions()} function. For LIBSVM this
will read the prediction files that is being written by LIBSVM to disk.

\subsection{Other functions}

Every wrapper should also be able to find tiself in a given directory tree.
For this \code{findSoftware} is provided.

At last, for querying reasons, there is also a print routine
so that wrapper can print out any further information about itself.
